---
title: "P8105_HW1_HL2710"
author: "Ainsel Levitskaia-Collins, HL2710"
date: "2025-09-17"
output: github_document
---

### Problem 1

The following code is used to download the `moderndive` library and the `early_january_weather` dataset:

```{r message = FALSE}
library("moderndive")
library("tidyverse")
data("early_january_weather")
```

#### Determining important information about `early_january_weather`

First, determining variable information about `early_january_weather`:

```{r results = FALSE}
str(early_january_weather)
```

Second, determining the size of `early_january_weather`:

```{r results = FALSE}
nrow(early_january_weather)
ncol(early_january_weather)
```

Third, determining the mean temperature of `early_january_weather`:

```{r results = FALSE}
mean(pull(early_january_weather, temp))
```

There are 15 variables in the `early_january_weather` dataset: the weather station 
which collected data (origin), the time of recording (year, month, day, hour), the 
temperature recorded in Fahrenheit (temp), the dewpoint in Fahrenheit (dewp), the relative humidity 
(humid), the wind direction in degrees (wind_dir), the speed and gust of wind in mph (wind_speed, 
wind_gust), the precipitation in inches (precip), the sea pressure in millibars (pressure), 
the visibility in miles (visib), and the date and hour of the recording (time_hour).

The dataset has 15 total columns (1 per variable) and 358 rows (1 per observation). The 
mean temperature recorded in the dataset is 39.6 degrees Fahrenheit.

#### Creating a scatterplot of `temp` vs `time`

First, create a scatterplot of `temp` vs `time`:

```{r}
ggp_early_jan_weather = 
  ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point()
```

Second, save the scatterplot of `temp` vs `time`:

```{r}
ggsave("ggp_early_jan_weather.pdf", ggp_early_jan_weather, width = 9, height = 5)
```

Third, display the scatterplot of `temp` vs `time`:

```{r}
ggp_early_jan_weather
```

The overall pattern of the scatterplot is that, within each day of the first half of January, 
there are natural variations of temperature and humidity. However, over the course of the 
half month, the average temperature and humidity levels increase.

### Problem 2

Creating a dataframe with a random normal sample of size 10, a logical vector indicating whether 
elements of the random sample are greater than 0, a character vector of length 10, and a factor 
vector of length 10 with 3 different factor "levels":

```{r}
variable_types_df = tibble(
  random_sample = rnorm(10),
  rs_gt_0 = random_sample > 0,
  random_chars = c("a", "c", "x", "d", "h", "g", "h", "i", "s", "r"),
  random_factor = factor(c("yes", "yes", "yes", "no", "no", "no", "unsure", "unsure", "unsure", "unsure"))
)
```

Trying to take the mean of each of these variables:

```{r results = FALSE, warning = FALSE}
mean(pull(variable_types_df, random_sample))
mean(pull(variable_types_df, rs_gt_0))
mean(pull(variable_types_df, random_chars))
mean(pull(variable_types_df, random_factor))
```

Taking the mean of the random sample (`random_sample`) and logical vector (`rs_gt_0`) variables
works successfully. However, taking the mean of the random character (`random_chars`) and 
random factor (`random_factor`) variables is unsuccessful.