---
title: "P8105_HW1_HL2710"
author: "Ainsel Levitskaia-Collins, HL2710"
date: "2025-09-17"
output: github_document
---

### Problem 1

Loading the `moderndive` library and the `early_january_weather` dataset:

```{r}
library("moderndive")
data("early_january_weather")
```

Determining important information about `early_january_weather` using a code chunk:

```{r message = FALSE, results = FALSE}
# Determining variable information about early_january_weather
str(early_january_weather)

# Determining the size of early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)

# Determining the mean temperature of early_january_weather
mean(early_january_weather$temp)
```

There are 15 variables in the `early_january_weather` dataset: the weather station 
which collected data (origin), the time of recording (year, month, day, hour), the 
temperature recorded in Fahrenheit (temp), the dewpoint in Fahrenheit (dewp), the relative humidity 
(humid), the wind direction in degrees (wind_dir), the speed and gust of wind in mph (wind_speed, 
wind_gust), the precipitation in inches (precip), the sea pressure in millibars (pressure), 
the visibility in miles (visib), and the date and hour of the recording (time_hour).

The dataset has 15 total columns (1 per variable) and 358 rows (1 per observation). The 
mean temperature recorded in the dataset is 39.6 degrees Fahrenheit.

### Problem 2

